maze-dataset: Maze Generation with Algorithmic Variety and Representational Flexibility

### 2025-04-09 docs/paper/paper.tex
minor fixes

This package utilizes a simple, efficient representation of mazes as
subgraphs of a finite lattice, which we call a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze}{\texttt{LatticeMaze}}.
Using an adjacency matrix for storing mazes would be memory inefficient
by failing to exploit the highly sparse structure -- for example, for a
2-dimensional maze, only 4 of the diagonals would be filled in. On the
other hand, using an adjacency list could lead to a poor lookup time for
whether any given connection exists.

>>>>

This package utilizes a simple, efficient representation of mazes as
subgraphs of a finite lattice, which we call a
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#LatticeMaze}{\texttt{LatticeMaze}}.
Using an adjacency matrix for storing mazes would be memory inefficient
by failing to exploit the highly sparse structure -- for example, for a
2-dimensional maze, only 4 off-diagonal bands would be have nonzero
values. On the other hand, using an adjacency list could lead to a poor
lookup time for whether any given connection exists.
